### 2006-02-16 inst/doc/MVCClass.Rnw
Added a slot to the graphView class and then had to update all the documentation.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@16287 bc3139a8-67e5-0310-9ffc-ced21a209358

The \Robject{sPlotView} class represents a scatterplot view and it has the
extra slots, dfRows, colx, and coly, where dfRows are the row names from the
model that are shown in the plot, colx is the column name from the model that
is shown as the x variable in the plot, and coly is the column name from the
model that is shown as the y variable in the plot.  The \Robject{graphView}
class represents a graph plot view and it contains no extra slots besides
those in the \Robject{plotView} class.  The \Robject{heatmapView} represents a
heatmap view of the data and it contains the slot, ordering, which is a list
that is returned from the \Rfunction{heatmap} function to give information
about the dendrogram ordering.  Note that some of these views are only
applicable for certain model types. For example, the \Robject{graphView} class
will only make sense for a view of a graph object, which would be stored in the
\Robject{graphModel} class.

>>>>

The \Robject{sPlotView} class represents a scatterplot view and it has the
extra slots, dfRows, colx, and coly, where dfRows are the row names from the
model that are shown in the plot, colx is the column name from the model that
is shown as the x variable in the plot, and coly is the column name from the
model that is shown as the y variable in the plot.  The \Robject{graphView}
class represents a graph plot view and it has the extra slot, grLayout, which
holds a \Robject{Ragraph} object that represents the layout of the graph plot.
The \Robject{heatmapView} represents a heatmap view of the data and it contains
the slot, ordering, which is a list that is returned from the
\Rfunction{heatmap} function to give information about the dendrogram
ordering.  Note that some of these views are only applicable for certain model
types.  For example, the \Robject{graphView} class will only make sense for a
view of a graph object, which would be stored in the \Robject{graphModel}
class.

### 2006-02-16 inst/paper/paper2.tex
Added a slot to the graphView class and then had to update all the documentation.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@16287 bc3139a8-67e5-0310-9ffc-ced21a209358

The \Rclass{sPlotView} class represents a scatter plot view and it has the
extra slots, \Rslot{dfRows}, \Rslot{xvar}, and \Rslot{yvar}, where
\Rslot{dfRows} are the row names from the model that are shown in the plot,
\Rslot{xvar} is the variable name from the model that is shown as the x
variable in the plot, and \Rslot{yvar} is the variable name from the model
that is shown as the y variable in the plot.  The \Rclass{graphView} class
represents a graph plot view and it contains no extra slots besides those in
the \Rclass{plotView} class.  The \Rclass{heatmapView} represents a heatmap
view of the data and it contains the slot, \Rslot{ordering}, which is a list
that is returned from the \Rfunction{heatmap} function to give information
about the ordering in the row and column dendrograms.  Note that some of these
views are only applicable for certain model types.  For example, the
\Rclass{graphView} class only makes sense for a view of a graph object,
which is stored in the \Rclass{graphModel} class.

>>>>

The \Rclass{sPlotView} class represents a scatter plot view and it has the
extra slots, \Rslot{dfRows}, \Rslot{xvar}, and \Rslot{yvar}, where
\Rslot{dfRows} are the row names from the model that are shown in the plot,
\Rslot{xvar} is the variable name from the model that is shown as the x
variable in the plot, and \Rslot{yvar} is the variable name from the model
that is shown as the y variable in the plot.  The \Rclass{graphView} class
represents a graph plot view and it contains the slot, \Rslot{grLayout}, which
holds a \Robject{Ragraph} object that represents the layout of the graph plot.
The \Rclass{heatmapView} represents a heatmap
view of the data and it contains the slot, \Rslot{ordering}, which is a list
that is returned from the \Rfunction{heatmap} function to give information
about the ordering in the row and column dendrograms.  Note that some of these
views are only applicable for certain model types.  For example, the
\Rclass{graphView} class only makes sense for a view of a graph object,
which is stored in the \Rclass{graphModel} class.
